Binocular integration of chromatic and luminance signals

### 2024-04-15 manuscript.qmd
Switched to using normalized contrast values

$^1$Department of Psychology, University of York, UK

$^2$York Biomedical Research Institute, University of York, UK

$^3$School of Psychology, University of Nottingham, UK

$^4$School of Philosophy, Psychology and Language Sciences, University of Edinburgh, UK

$^*$Corresponding author, email: daniel.baker\@york.ac.uk

@@

if (processdata>0){
  install_python(version="3.6")
  # use_python_version("3.9.19")
  # use_python('/usr/bin/python3.9')
  # install_miniconda()
  # use_miniconda('r-reticulate')
  # py_install('pip')
  py_install('https://github.com/wichmann-lab/python-psignifit/zipball/master')
  # install psignifit in the terminal with:
  # sudo pip install https://github.com/wichmann-lab/python-psignifit/zipball/master
  ps <- import('psignifit')
  # calculate constant to scale the slope parameter to the Gaussian SD
  C <- ps$utils$my_norminv(1-0.05,0,1) - ps$utils$my_norminv(0.05,0,1)
}

@@

sublist <- unique(ex1data$Subject)
explist <- unique(ex1data$Experiment)

@@

# now also pool across subjects and fit for plotting the full posterior
for (cond in 1:12){
  datatofit <- data.frame(contrastsdB[1,cond,],colSums(ncorrect[,cond,]),colSums(ntrials[,cond,]))
  colnames(datatofit) <- c('CdB','Ncorrect','Ntrials')
  res <- ps$psignifit(as.matrix(datatofit),options)

@@

  allposteriors[cond,,] <- sumpos
  allposX[cond,] <- xycos[[1]]
  allposY[cond,] <- xycos[[2]]

save(file='local/MCSdata.RData',list=c('MCSthresh','MCSslope','thdelev','slopematrix','detslopes','MCSpropcorr','contrastsdB','allposteriors','allposX','allposY'))

@@

@@

pedlist <<- seq(-12,30,6)
allp <- matrix(0,nrow=4,ncol=7)
allparams <- array(0,dim=c(4,ntotalsimplexfits,8))
allrms <- NULL
 for (cond in 1:3){
   print(cond)
   datatofit <<- meanthresh[cond,,]

@@

   pedlist <<- seq(-6,36,6)  # increase pedestal contrasts for the chromatic conditions

@@

# finally fit the disc data
pedlist <<- seq(-12,30,6)
cond <- 4

   print(cond)
   datatofit <<- meanthresh3

@@

stopCluster(cluster)

@@

@@

pedlist <- -12:39
pedlevelsC <- 10^(pedlist/20)
pedlevelsC[1] <- 0
allpred <- array(0,dim=c(4,4,length(pedlist)))

@@

ticklocsx <- seq(-12,36,6)
ticklabelsx <- c(0,0.5,1,2,4,8,16,32,64)
ticklocsy <- seq(-12,36,6)
ticklabelsy <- c(0.25,0.5,1,2,4,8,16,32,64)
pedcontrasts <- seq(-12,30,6)

exptorder <- c(1,3,2)
paneltitles <- c('(a) Achromatic thresholds','(b) Red/Green thresholds','(c) Blue/Yellow thresholds')
par(mfrow=c(2,3))
for (expt in 1:3){
par(pty="s")  # make axis square
plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=c(-12,36), ylim=c(-12,39))   
axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)     # plot tick marks (no labels)
axis(2, at=ticklocsy, tck=0.01, lab=F, lwd=2)
mtext(text = ticklabelsx, side = 1, at=ticklocsx, line=0.3)     
mtext(text = ticklabelsy, side = 2, at=ticklocsy, line=0.2, las=1)
title(xlab="Pedestal contrast (%)", col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)   
title(ylab="Threshold (%)", col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)
title(main=paneltitles[expt],cex.main=2.5)

for (cond in 1:4){
  arrows(pedcontrasts,meanthresh[exptorder[expt],cond,],pedcontrasts,meanthresh[exptorder[expt],cond,]+SEthresh[exptorder[expt],cond,],col=collist[cond],angle=90,length=0.02,lwd=2)
 arrows(pedcontrasts,meanthresh[exptorder[expt],cond,],pedcontrasts,meanthresh[exptorder[expt],cond,]-SEthresh[exptorder[expt],cond,],col=collist[cond],angle=90,length=0.02,lwd=2)  
  # lines(pedcontrasts,meanthresh[1,cond,],col=collist[cond],lwd=2)
  lines(pedlist,allpreddB[exptorder[expt],cond,],col=collist[cond],lwd=2)
  points(pedcontrasts,meanthresh[exptorder[expt],cond,],pch=16,col=collist[cond],cex=1.5)
}
text(24,-9,paste0('RMSE = ',round(allrms[expt],digits=2),'dB'),cex=2)
if (expt==1){legend(-12,36,c('Monocular','Binocular','Half-binocular','Dichoptic'),pch=16,col=collist,box.lwd=2,cex=1.5)}

pedcontrasts <- c(-12,seq(0,36,6))  # update pedestal contrasts for plotting chromatic conditions

@@

par(pty="s")  # make axis square
plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=c(-12,36), ylim=c(-6,18))   
axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)     # plot tick marks (no labels)
axis(2, at=ticklocsy, tck=0.01, lab=F, lwd=2)
mtext(text = ticklabelsx, side = 1, at=ticklocsx, line=0.3)     
mtext(text = ticklabelsy, side = 2, at=ticklocsy, line=0.2, las=1)
title(xlab="Pedestal contrast (%)", col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)   
title(ylab=expression(paste('Weibull ', beta)), col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)
title(main=paneltitles[expt],cex.main=2.5)

@@

pdf('Figures/discdata.pdf',width=13,height=7)

par(mfcol=c(1,2))
pedcontrasts <- seq(-12,30,6)

ticklocsy <- seq(-18,30,6)
ticklabelsy <- c(0.125,0.25,0.5,1,2,4,8,16,32)

par(pty="s")  # make axis square
plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=c(-12,36), ylim=c(-18,30))   
axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)     # plot tick marks (no labels)
axis(2, at=ticklocsy, tck=0.01, lab=F, lwd=2)
mtext(text = ticklabelsx, side = 1, at=ticklocsx, line=0.3)     
mtext(text = ticklabelsy, side = 2, at=ticklocsy, line=0.2, las=1)
title(xlab="Pedestal contrast (%)", col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)   
title(ylab="Threshold (%)", col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)
title(main='(a) Flickering disc (thresholds)',cex.main=2)

for (cond in 1:4){
  arrows(pedcontrasts,meanthresh3[cond,],pedcontrasts,meanthresh3[cond,]+SEthresh3[cond,],col=collist[cond],angle=90,length=0.02,lwd=2)
 arrows(pedcontrasts,meanthresh3[cond,],pedcontrasts,meanthresh3[cond,]-SEthresh3[cond,],col=collist[cond],angle=90,length=0.02,lwd=2)  
  # lines(pedcontrasts,meanthresh[1,cond,],col=collist[cond],lwd=2)
  lines(pedlist,allpreddB[4,cond,],col=collist[cond],lwd=2)
  points(pedcontrasts,meanthresh3[cond,],pch=16,col=collist[cond],cex=1.5)
}
text(24,-15,paste0('RMSE = ',round(allrms[4],digits=2),'dB'),cex=2)
legend(-12,30,c('Monocular','Binocular','Half-binocular','Dichoptic'),pch=16,col=collist,box.lwd=2,cex=1.5)

@@

par(pty="s")  # make axis square
plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=c(-12,36), ylim=c(-6,18))   
axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)     # plot tick marks (no labels)
axis(2, at=ticklocsy, tck=0.01, lab=F, lwd=2)
mtext(text = ticklabelsx, side = 1, at=ticklocsx, line=0.3)     
mtext(text = ticklabelsy, side = 2, at=ticklocsy, line=0.2, las=1)
title(xlab="Pedestal contrast (%)", col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)   
title(ylab=expression(paste('Weibull ', beta)), col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)
title(main='(b) Flickering disc (slopes)',cex.main=2)

@@

```{r stanmodelspecifications, include=FALSE}

modelString = "
  data {
    int<lower=1> Ndatasets ;
    int<lower=1> Ntotal ;
    int ncorrect[Ntotal] ;
    int ntrials[Ntotal] ;
    real PedestalContrast[Ntotal] ;
    real TargetContrast[Ntotal] ;
    int<lower=1> c[Ntotal] ;
    int<lower=1> s[Ntotal] ;  
  }
  parameters {
    vector<lower=0.1, upper=3>[Ndatasets] p;
    vector<lower=2, upper=8>[Ndatasets] q;
    vector<lower=0.5, upper=2>[Ndatasets] m;
    vector<lower=0.001, upper=2>[Ndatasets] S;  
    vector<lower=0.001, upper=2>[Ndatasets] Z;
    vector<lower=0.001, upper=2>[Ndatasets] w;
    vector<lower=0.001, upper=2>[Ndatasets] k;

    real<lower=0> sigma ;
    real<lower=0.1, upper=3> pmu ; 
    real<lower=2, upper=8> qmu ; 
    real<lower=0.5, upper=2> mmu ;
    real<lower=0.001, upper=2> Smu ;
    real<lower=0.001, upper=2> Zmu ; 
    real<lower=0.001, upper=2> wmu ; 
    real<lower=0.001, upper=2> kmu ;

@@

    pmu ~ normal( 1.4 , 0.1 ) ;
    qmu ~ normal( 6.59 , 0.5 ) ;
    mmu ~ normal( 1.28 , 0.2 ) ;
    Smu ~ normal( 0.985 , 0.2 ) ;
    Zmu ~ normal( 0.08 , 0.5 ) ;
    wmu ~ normal( 1 , 0.2 ) ;
    kmu ~ normal( 0.194 , 0.1 ) ;
    sigma ~ uniform( 1.0E-3 , 1.0E+3 ) ;
    psigma ~ uniform( 1.0E-3 , 1.0E+3 ) ;
    qsigma ~ uniform( 1.0E-3 , 1.0E+3 ) ;
    msigma ~ uniform( 1.0E-3 , 1.0E+3 ) ;
    Ssigma ~ uniform( 1.0E-3 , 1.0E+3 ) ;
    Zsigma ~ uniform( 1.0E-3 , 1.0E+3 ) ;    
    wsigma ~ uniform( 1.0E-3 , 1.0E+3 ) ;
    ksigma ~ uniform( 1.0E-3 , 1.0E+3 ) ;

@@

crossmodelString = "
  data {
    int<lower=1> Ndatasets ;
    int<lower=1> Ntotal ;
    int ncorrect[Ntotal] ;
    int ntrials[Ntotal] ;
    real PedestalContrast[Ntotal] ;
    real TargetContrast[Ntotal] ;
    int<lower=1> c[Ntotal] ;
    int<lower=1> s[Ntotal] ;  
  }
  parameters {
    vector<lower=0, upper=40>[Ndatasets] Zac;
    vector<lower=0, upper=40>[Ndatasets] Zrg;
    vector<lower=0, upper=40>[Ndatasets] Zby;
    vector<lower=0.001, upper=2>[Ndatasets] wAcR;
    vector<lower=0.001, upper=2>[Ndatasets] wAcB;
    vector<lower=0.001, upper=2>[Ndatasets] wRgA;
    vector<lower=0.001, upper=2>[Ndatasets] wRgB;
    vector<lower=0.001, upper=2>[Ndatasets] wByA;
    vector<lower=0.001, upper=2>[Ndatasets] wByR;

    real<lower=0> sigma ;
    real<lower=0, upper=40> Zacmu ; 
    real<lower=0, upper=40> Zrgmu ; 
    real<lower=0, upper=40> Zbymu ; 
    real<lower=0.001, upper=2> wAcRmu ; 
    real<lower=0.001, upper=2> wAcBmu ; 
    real<lower=0.001, upper=2> wRgAmu ; 
    real<lower=0.001, upper=2> wRgBmu ; 
    real<lower=0.001, upper=2> wByAmu ; 
    real<lower=0.001, upper=2> wByRmu ;

    real<lower=0> Zacsigma ;    
    real<lower=0> Zrgsigma ;    
    real<lower=0> Zbysigma ;    
    real<lower=0> wAcRsigma ;
    real<lower=0> wAcBsigma ;
    real<lower=0> wRgAsigma ;
    real<lower=0> wRgBsigma ;
    real<lower=0> wByAsigma ;
    real<lower=0> wByRsigma ;
  }
  model {
    Zacmu ~ normal( 10 , 5 ) ;
    Zrgmu ~ normal( 10 , 5 ) ;
    Zbymu ~ normal( 10 , 5 ) ;
    wAcRmu ~ normal( 0.5 , 0.3 ) ;
    wAcBmu ~ normal( 0.5 , 0.3 ) ;
    wRgAmu ~ normal( 0.5 , 0.3 ) ;
    wRgBmu ~ normal( 0.5 , 0.3 ) ;
    wByAmu ~ normal( 0.5 , 0.3 ) ;
    wByRmu ~ normal( 0.5 , 0.3 ) ;
    sigma ~ uniform( 1.0E-3 , 1.0E+3 ) ;
    Zacsigma ~ uniform( 1.0E-3 , 1.0E+3 ) ;    
    Zrgsigma ~ uniform( 1.0E-3 , 1.0E+3 ) ;    
    Zbysigma ~ uniform( 1.0E-3 , 1.0E+3 ) ;    
    wAcRsigma ~ uniform( 1.0E-3 , 1.0E+3 ) ;
    wAcBsigma ~ uniform( 1.0E-3 , 1.0E+3 ) ;
    wRgAsigma ~ uniform( 1.0E-3 , 1.0E+3 ) ;
    wRgBsigma ~ uniform( 1.0E-3 , 1.0E+3 ) ;
    wByAsigma ~ uniform( 1.0E-3 , 1.0E+3 ) ;
    wByRsigma ~ uniform( 1.0E-3 , 1.0E+3 ) ;

    Zac ~ normal( Zacmu , Zacsigma ) ; // vectorized
    Zrg ~ normal( Zrgmu , Zrgsigma ) ; // vectorized
    Zby ~ normal( Zbymu , Zbysigma ) ; // vectorized
    wAcR ~ normal( wAcRmu , wAcRsigma ) ; // vectorized
    wAcB ~ normal( wAcBmu , wAcBsigma ) ; // vectorized
    wRgA ~ normal( wRgAmu , wRgAsigma ) ; // vectorized
    wRgB ~ normal( wRgBmu , wRgBsigma ) ; // vectorized
    wByA ~ normal( wByAmu , wByAsigma ) ; // vectorized
    wByR ~ normal( wByRmu , wByRsigma ) ; // vectorized

    if (c[i]==1) { // achromatic detection condition
    Lt = pow(TargetContrast[i],1.21) / (1.03 + (TargetContrast[i])) ;
    Rt = 0 ;
    Ln = 0 ;
    Rn = 0 ;

    targresp = pow((Lt + Rt), 7.82) / (Zac[s[i]] + pow((Lt + Rt), 6.4)) ;
    nullresp = pow((Ln + Rn), 7.82) / (Zac[s[i]] + pow((Ln + Rn), 6.4)) ;

    if (c[i]==2) { // red/green detection condition
    Lt = pow(TargetContrast[i],1.21) / (1.03 + (TargetContrast[i])) ;
    Rt = 0 ;
    Ln = 0 ;
    Rn = 0 ;

    targresp = pow((Lt + Rt), 7.82) / (Zrg[s[i]] + pow((Lt + Rt), 6.4)) ;
    nullresp = pow((Ln + Rn), 7.82) / (Zrg[s[i]] + pow((Ln + Rn), 6.4)) ;

    if (c[i]==3) { // blue/yellow detection condition
    Lt = pow(TargetContrast[i],1.21) / (1.03 + (TargetContrast[i])) ;
    Rt = 0 ;
    Ln = 0 ;
    Rn = 0 ;

    targresp = pow((Lt + Rt), 7.82) / (Zby[s[i]] + pow((Lt + Rt), 6.4)) ;
    nullresp = pow((Ln + Rn), 7.82) / (Zby[s[i]] + pow((Ln + Rn), 6.4)) ;

    if (c[i]==4) { // achromatic target, achromatic mask
      Lt = pow(TargetContrast[i],1.21) / (1.03 + TargetContrast[i] + 1*PedestalContrast[i]) ;
      Rt = pow(PedestalContrast[i],1.21) / (1.03 + PedestalContrast[i] + 1*TargetContrast[i]) ;
      Ln = 0 ;
      Rn = pow(PedestalContrast[i],1.21) / (1.03 + PedestalContrast[i]) ;

      targresp = pow((Lt + Rt), 7.82) / (Zac[s[i]] + pow((Lt + Rt), 6.4)) ;
      nullresp = pow((Ln + Rn), 7.82) / (Zac[s[i]] + pow((Ln + Rn), 6.4)) ;

    if (c[i]==5) { // red/green target, achromatic mask
      Lt = pow(TargetContrast[i],1.21) / (1.03 + TargetContrast[i] + wRgA[s[i]]*PedestalContrast[i]) ;
      Rt = 0 ;
      Ln = 0 ;
      Rn = 0 ;

      targresp = pow((Lt + Rt), 7.82) / (Zrg[s[i]] + pow((Lt + Rt), 6.4)) ;
      nullresp = pow((Ln + Rn), 7.82) / (Zrg[s[i]] + pow((Ln + Rn), 6.4)) ;     
    }

    if (c[i]==6) { // blue/yellow target, achromatic mask
      Lt = pow(TargetContrast[i],1.21) / (1.03 + TargetContrast[i] + wByA[s[i]]*PedestalContrast[i]) ;
      Rt = 0 ;
      Ln = 0 ;
      Rn = 0 ;

      targresp = pow((Lt + Rt), 7.82) / (Zby[s[i]] + pow((Lt + Rt), 6.4)) ;
      nullresp = pow((Ln + Rn), 7.82) / (Zby[s[i]] + pow((Ln + Rn), 6.4)) ;     
    }

    if (c[i]==7) { // achromatic target, red/green mask
      Lt = pow(TargetContrast[i],1.21) / (1.03 + TargetContrast[i] + wAcR[s[i]]*PedestalContrast[i]) ;
      Rt = 0 ;
      Ln = 0 ;
      Rn = 0 ;

      targresp = pow((Lt + Rt), 7.82) / (Zac[s[i]] + pow((Lt + Rt), 6.4)) ;
      nullresp = pow((Ln + Rn), 7.82) / (Zac[s[i]] + pow((Ln + Rn), 6.4)) ;

    if (c[i]==8) { // red/green target, red/green mask
      Lt = pow(TargetContrast[i],1.21) / (1.03 + TargetContrast[i] + 1*PedestalContrast[i]) ;
      Rt = pow(PedestalContrast[i],1.21) / (1.03 + PedestalContrast[i] + 1*TargetContrast[i]) ;
      Ln = 0 ;
      Rn = pow(PedestalContrast[i],1.21) / (1.03 + PedestalContrast[i]) ;

      targresp = pow((Lt + Rt), 7.82) / (Zrg[s[i]] + pow((Lt + Rt), 6.4)) ;
      nullresp = pow((Ln + Rn), 7.82) / (Zrg[s[i]] + pow((Ln + Rn), 6.4)) ;     
    }

    if (c[i]==9) { // blue/yellow target, red/green mask
      Lt = pow(TargetContrast[i],1.21) / (1.03 + TargetContrast[i] + wByR[s[i]]*PedestalContrast[i]) ;
      Rt = 0 ;
      Ln = 0 ;
      Rn = 0 ;

      targresp = pow((Lt + Rt), 7.82) / (Zby[s[i]] + pow((Lt + Rt), 6.4)) ;
      nullresp = pow((Ln + Rn), 7.82) / (Zby[s[i]] + pow((Ln + Rn), 6.4)) ;     
    }

     if (c[i]==10) { // achromatic target, blue/yellow mask
      Lt = pow(TargetContrast[i],1.21) / (1.03 + TargetContrast[i] + wAcB[s[i]]*PedestalContrast[i]) ;
      Rt = 0 ;
      Ln = 0 ;
      Rn = 0 ;

      targresp = pow((Lt + Rt), 7.82) / (Zac[s[i]] + pow((Lt + Rt), 6.4)) ;
      nullresp = pow((Ln + Rn), 7.82) / (Zac[s[i]] + pow((Ln + Rn), 6.4)) ;

    if (c[i]==11) { // red/green target, blue/yellow mask
      Lt = pow(TargetContrast[i],1.21) / (1.03 + TargetContrast[i] + wRgB[s[i]]*PedestalContrast[i]) ;
      Rt = 0 ;
      Ln = 0 ;
      Rn = 0 ;

      targresp = pow((Lt + Rt), 7.82) / (Zrg[s[i]] + pow((Lt + Rt), 6.4)) ;
      nullresp = pow((Ln + Rn), 7.82) / (Zrg[s[i]] + pow((Ln + Rn), 6.4)) ;     
    }

    if (c[i]==12) { // blue/yellow target, blue/yellow mask
      Lt = pow(TargetContrast[i],1.21) / (1.03 + TargetContrast[i] + 1*PedestalContrast[i]) ;
     Rt = pow(PedestalContrast[i],1.21) / (1.03 + PedestalContrast[i] + 1*TargetContrast[i]) ;
      Ln = 0 ;
      Rn = pow(PedestalContrast[i],1.21) / (1.03 + PedestalContrast[i]) ;

      targresp = pow((Lt + Rt), 7.82) / (Zby[s[i]] + pow((Lt + Rt), 6.4)) ;
      nullresp = pow((Ln + Rn), 7.82) / (Zby[s[i]] + pow((Ln + Rn), 6.4)) ;     
    }

    dprime = (targresp-nullresp)/0.23 ;
    if (is_nan(dprime)){
       dprime = 0;
    }
    if (is_inf(dprime)){
       dprime = 10;
    }
    if (dprime > 10){
       dprime = 10;
    }    
    ncorrect[i] ~ binomial(ntrials[i], Phi(dprime/sqrt(2))) ;
    }
  }  
" # close quote for modelString

@@

@@

>>>>

$^1$Department of Psychology, University of York, UK\
$^2$York Biomedical Research Institute, University of York, UK\
$^3$School of Psychology, University of Nottingham, UK\
$^4$School of Philosophy, Psychology and Language Sciences, University of Edinburgh, UK\
$^*$Corresponding author, email: daniel.baker\@york.ac.uk

@@

if (processdata>0){
  # install_python(version="3.6")
  # py_install('https://github.com/wichmann-lab/python-psignifit/zipball/master')

  use_miniconda('r-reticulate')

  # install psignifit in the terminal with:
  # sudo pip install https://github.com/wichmann-lab/python-psignifit/zipball/master
  ps <- import('psignifit')
  # calculate constant to scale the slope parameter to the Gaussian SD
  C <- ps$utils$my_norminv(1-0.05,0,1) - ps$utils$my_norminv(0.05,0,1)
}

@@

sublist <- unique(ex1data$Subject)
explist <- c('AC','RG','BY')  # hard coded in this order to avoid confusion later on

@@

pooledthresh <- NULL
# now also pool across subjects and fit for plotting the full posterior
for (cond in 1:12){
  datatofit <- data.frame(contrastsdB[1,cond,],colSums(ncorrect[,cond,]),colSums(ntrials[,cond,]))
  colnames(datatofit) <- c('CdB','Ncorrect','Ntrials')
  res <- ps$psignifit(as.matrix(datatofit),options)

@@

  allposteriors[cond,,] <- sumpos
  allposX[cond,] <- xycos[[1]]
  allposY[cond,] <- xycos[[2]]
  pooledthresh[cond] <- res$Fit[1]
}

save(file='local/MCSdata.RData',list=c('MCSthresh','MCSslope','thdelev','slopematrix','detslopes','MCSpropcorr','contrastsdB','allposteriors','allposX','allposY','pooledthresh'))

@@

temp <- array(0,dim=c(4,4,8))
temp[1,,] <- meanthresh[1,,]
temp[2,,] <- meanthresh[2,,]
temp[3,,] <- meanthresh[3,,]
temp[4,,] <- meanthresh3
meanthresh <- temp

scalefactdB <- meanthresh[,1,1]
scalefact <- 10^(scalefactdB/20)

@@

allp <- matrix(0,nrow=4,ncol=7)
allparams <- array(0,dim=c(4,ntotalsimplexfits,8))
allrms <- NULL
for (cond in 1:4){
  print(cond)
  if (cond==1){pedlist <<- seq(-12,30,6) - scalefactdB[cond]}
  if (cond==2){pedlist <<- seq(-6,36,6) - scalefactdB[cond]}
  if (cond==3){pedlist <<- seq(-6,36,6) - scalefactdB[cond]}
  if (cond==4){pedlist <<- seq(-12,30,6) - scalefactdB[cond]}

  datatofit <<- meanthresh[cond,,] - scalefactdB[cond]

@@

@@

@@

stopCluster(cluster)
}

@@

  scalefactdB <- c(meanthresh[,1,1],meanthresh3[1,1])
  scalefact <- 10^(scalefactdB/20)

@@

  pedlist <- -24:39
  pedlevelsC <- 10^(pedlist/20)
  pedlevelsC[1] <- 0
  allpred <- array(0,dim=c(4,4,length(pedlist)))

@@

  paneltitles <- c('(a) Achromatic thresholds','(b) Red/Green thresholds','(c) Blue/Yellow thresholds')
  par(mfrow=c(2,3))
  for (expt in 1:3){

    ticklocsx <- seq(-24,30,6)
    ticklabelsx <- c(0,'1/8','1/4','1/2',1,2,4,8,16,32)
    ticklocsy <- seq(-24,30,6)
    ticklabelsy <- c('1/16','1/8','1/4','1/2',1,2,4,8,16,32)

    par(pty="s")  # make axis square
    plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=c(min(ticklocsx),max(ticklocsx)), ylim=c(min(ticklocsy),max(ticklocsy)))   
    axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)     # plot tick marks (no labels)
    axis(2, at=ticklocsy, tck=0.01, lab=F, lwd=2)
    mtext(text = ticklabelsx, side = 1, at=ticklocsx, line=0.3)     
    mtext(text = ticklabelsy, side = 2, at=ticklocsy, line=0.2, las=1)
    title(xlab='Normalized pedestal contrast', col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)   
    title(ylab='Normalized threshold contrast', col.lab=rgb(0,0,0), line=1.8, cex.lab=1.5)
    title(main=paneltitles[expt],cex.main=2.5)

    if (expt==1){pedcontrasts <- seq(-12,30,6) - scalefactdB[expt]}
    if (expt>1){pedcontrasts <- seq(-6,36,6) - scalefactdB[expt]}
    pedcontrasts[1] <- min(ticklocsx)

    for (cond in 1:4){
      arrows(pedcontrasts,meanthresh[expt,cond,]-scalefactdB[expt],pedcontrasts,meanthresh[expt,cond,]-scalefactdB[expt]+SEthresh[expt,cond,],col=collist[cond],angle=90,length=0.02,lwd=2)
      arrows(pedcontrasts,meanthresh[expt,cond,]-scalefactdB[expt],pedcontrasts,meanthresh[expt,cond,]-scalefactdB[expt]-SEthresh[expt,cond,],col=collist[cond],angle=90,length=0.02,lwd=2)  
      # lines(pedcontrasts,meanthresh[1,cond,],col=collist[cond],lwd=2)
      lines(pedlist,allpreddB[expt,cond,],col=collist[cond],lwd=2)
      points(pedcontrasts,meanthresh[expt,cond,]-scalefactdB[expt],pch=16,col=collist[cond],cex=1.5)
    }
    text(ticklocsx[7]+3,ticklocsy[1]+3,paste0('RMSE = ',round(allrms[expt],digits=2),'dB'),cex=2)
    if (expt==1){legend(-24,30,c('Monocular','Binocular','Half-binocular','Dichoptic'),pch=16,col=collist,box.lwd=2,cex=1.5)}

@@

    ticklocsx <- seq(-24,30,6)
    ticklabelsx <- c(0,'1/8','1/4','1/2',1,2,4,8,16,32)

    if (expt==1){pedcontrasts <- seq(-12,30,6) - scalefactdB[expt]}
    if (expt>1){pedcontrasts <- seq(-6,36,6) - scalefactdB[expt]}
    pedcontrasts[1] <- min(ticklocsx)

    par(pty="s")  # make axis square
    plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=c(min(ticklocsx),max(ticklocsx)), ylim=c(-6,18))   
    axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)     # plot tick marks (no labels)
    axis(2, at=ticklocsy, tck=0.01, lab=F, lwd=2)
    mtext(text = ticklabelsx, side = 1, at=ticklocsx, line=0.3)     
    mtext(text = ticklabelsy, side = 2, at=ticklocsy, line=0.2, las=1)
    title(xlab='Normalized pedestal contrast', col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)   
    title(ylab=expression(paste('Weibull ', beta)), col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)
    title(main=paneltitles[expt],cex.main=2.5)

@@

  pdf('Figures/discdata.pdf',width=10,height=6)

  par(mfcol=c(1,2))
  pedcontrasts <- seq(-12,30,6) - scalefactdB[4]
  pedcontrasts[1] <- -24

  ticklocsx <- seq(-24,30,6)
  ticklabelsx <- c(0,'1/8','1/4','1/2',1,2,4,8,16,32)
  ticklocsy <- seq(-24,30,6)
  ticklabelsy <- c('1/16','1/8','1/4','1/2',1,2,4,8,16,32)

  par(pty="s")  # make axis square
  plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=c(-24,30), ylim=c(-24,30))   
  axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)     # plot tick marks (no labels)
  axis(2, at=ticklocsy, tck=0.01, lab=F, lwd=2)
  mtext(text = ticklabelsx, side = 1, at=ticklocsx, line=0.3)     
  mtext(text = ticklabelsy, side = 2, at=ticklocsy, line=0.2, las=1)
  title(xlab="Normalized pedestal contrast (%)", col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)   
  title(ylab="Normalized threshold (%)", col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)
  title(main='(a) Flickering disc (thresholds)',cex.main=1.5)

  for (cond in 1:4){
    arrows(pedcontrasts,meanthresh3[cond,]-scalefactdB[4],pedcontrasts,meanthresh3[cond,]-scalefactdB[4]+SEthresh3[cond,],col=collist[cond],angle=90,length=0.02,lwd=2)
    arrows(pedcontrasts,meanthresh3[cond,]-scalefactdB[4],pedcontrasts,meanthresh3[cond,]-scalefactdB[4]-SEthresh3[cond,],col=collist[cond],angle=90,length=0.02,lwd=2)  
    # lines(pedcontrasts,meanthresh[1,cond,],col=collist[cond],lwd=2)
    lines(pedlist,allpreddB[4,cond,],col=collist[cond],lwd=2)
    points(pedcontrasts,meanthresh3[cond,]-scalefactdB[4],pch=16,col=collist[cond],cex=1.5)
  }
  text(ticklocsx[7]+3,ticklocsy[1]+3,paste0('RMSE = ',round(allrms[4],digits=2),'dB'),cex=1.5)
  legend(-24,30,c('Monocular','Binocular','Half-binocular','Dichoptic'),pch=16,col=collist,box.lwd=2,cex=1.2)

@@

  par(pty="s")  # make axis square
  plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=c(-24,30), ylim=c(-6,18))   
  axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)     # plot tick marks (no labels)
  axis(2, at=ticklocsy, tck=0.01, lab=F, lwd=2)
  mtext(text = ticklabelsx, side = 1, at=ticklocsx, line=0.3)     
  mtext(text = ticklabelsy, side = 2, at=ticklocsy, line=0.2, las=1)
  title(xlab="Normalized pedestal contrast (%)", col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)   
  title(ylab=expression(paste('Weibull ', beta)), col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)
  title(main='(b) Flickering disc (slopes)',cex.main=1.5)

@@

```{r stanmodelspecification, include=FALSE}

modelString = "
  data {
    int<lower=1> Ndatasets ;
    int<lower=1> Ntotal ;
    int ncorrect[Ntotal] ;
    int ntrials[Ntotal] ;
    real PedestalContrast[Ntotal] ;
    real TargetContrast[Ntotal] ;
    int<lower=1> c[Ntotal] ;
    int<lower=1> s[Ntotal] ;  
  }
  parameters {
    vector<lower=1, upper=3>[Ndatasets] p;
    vector<lower=2, upper=16>[Ndatasets] q;
    vector<lower=0.5, upper=2>[Ndatasets] m;
    vector<lower=0, upper=2>[Ndatasets] S;  
    vector<lower=0, upper=1>[Ndatasets] Z;
    vector<lower=0, upper=2>[Ndatasets] w;
    vector<lower=0, upper=2>[Ndatasets] k;

    real<lower=0> sigma ;
    real<lower=1, upper=3> pmu ; 
    real<lower=2, upper=16> qmu ; 
    real<lower=0.5, upper=2> mmu ;
    real<lower=0, upper=2> Smu ;
    real<lower=0, upper=1> Zmu ; 
    real<lower=0, upper=2> wmu ; 
    real<lower=0, upper=2> kmu ;

@@

    pmu ~ normal( 1.4 , 0.2 ) ;
    qmu ~ normal( 6.59 , 2 ) ;
    mmu ~ normal( 1.28 , 0.2 ) ;
    Smu ~ uniform( 0, 2 ) ;
    Zmu ~ uniform( 0, 1 ) ;
    wmu ~ normal( 1 , 0.2 ) ;
    kmu ~ uniform( 0, 2 ) ;
    sigma ~ uniform( 1.0E-3 , 1.0E+3 ) ;
    psigma ~ uniform( 1.0E-3 , 1.0E+3 ) ;
    qsigma ~ uniform( 1.0E-3 , 1.0E+3 ) ;
    msigma ~ uniform( 1.0E-3 , 1.0E+3 ) ;
    Ssigma ~ uniform( 1.0E-3 , 1.0E+3 ) ;
    Zsigma ~ uniform( 1.0E-3 , 1.0E+3 ) ;    
    wsigma ~ uniform( 1.0E-3 , 1.0E+3 ) ;
    ksigma ~ uniform( 1.0E-3 , 1.0E+3 ) ;

@@

@@

load('local/thresholddata.RData')
load('local/thresholddataDisc.RData')
scalefactdB <- c(meanthresh[,1,1],meanthresh3[1,1])
scalefact <- 10^(scalefactdB/20)
scalefactind <- 10^(cbind(allthresh[,,1,1],allthresh3[,1,1])/20)

@@

```{r stanmodelspecification2, include=FALSE}
